SCP Briefing Plots - Combined Intervention

### 2024-09-23 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Small changes to plotting script

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_27_scot_XGB_scaled/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_29_scot_scaled_skew_GOOD/"
#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

  plot_data_confint <- plot_data %>%
    group_by(year, income_quintile) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF12),
              margin_SF12 = qt(0.975, df = n - 1) * (sd(diff_SF12) / sqrt(n)),
              lower_SF12 = mean_SF12_change - margin_SF12,
              upper_SF12 = mean_SF12_change + margin_SF12) %>%
    mutate(
      mean_SF12_change = if_else(income_quintile %in% c(4, 5), 0, mean_SF12_change),
      margin_SF12 = if_else(income_quintile %in% c(4, 5), 0, margin_SF12),
      lower_SF12 = if_else(income_quintile %in% c(4, 5), 0, lower_SF12),
      upper_SF12 = if_else(income_quintile %in% c(4, 5), 0, upper_SF12)
    )

>>>>

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/old/old_33_scot_clipped/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_27_scot_XGB_scaled/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_29_scot_scaled_skew_GOOD/"
#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

  plot_data_confint <- plot_data %>%
    group_by(year, income_quintile) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF12),
              margin_SF12 = qt(0.975, df = n - 1) * (sd(diff_SF12) / sqrt(n)),
              lower_SF12 = mean_SF12_change - margin_SF12,
              upper_SF12 = mean_SF12_change + margin_SF12) %>%
    mutate(
      mean_SF12_change = if_else(income_quintile %in% c(4, 5), 0, mean_SF12_change),
      margin_SF12 = if_else(income_quintile %in% c(4, 5), 0, margin_SF12)
    )

  # lower_SF12 = if_else(income_quintile %in% c(4, 5), 0, lower_SF12),
  # upper_SF12 = if_else(income_quintile %in% c(4, 5), 0, upper_SF12)
